### 2023-05-09 my_paper/Hadah-last-names.tex
finish implementing the code that would merge synthetic parents (ACS) to children (CPS) addressing Yona's comments

\begin{center}
\begin{figure}
\caption{Inter-racial marriages as a percent of all marriages \\
 in the United States from 1995 to 2020.}
\includegraphics[width=\textwidth]{interracialovertime.png} 
\label{fig:3}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}
\caption{Distribution of the four types of children.}
\includegraphics[width=\textwidth]{PirChart2.png} 
\label{fig:dist}
\end{figure}
\end{center}

\newpage
\begin{center}
\begin{figure}
\caption{Chart explaining which synthetic parents and children \\
and when we observe them.}
\begin{tikzpicture}[node distance =2cm]
\node (start) [startstop] {Synthetic Parents: Observed in 1970 to 1990. $25 \leq age \leq 40$};

\node (pro1) [process, below of = start, yshift = -2cm] {Children: Observed between 1994 and 2019. Born between 1970 to 1990 and $25 \leq age \leq 40$};

\draw [arrow] (start) -- (pro1);
\end{tikzpicture}
\label{flowchart1}
\end{figure}
\end{center}

>>>>

\begin{center}
\begin{figure}[h!]
\caption{Inter-racial marriages as a percent of all marriages \\
 in the United States from 1995 to 2020.}
\includegraphics[width=\textwidth]{interracialovertime.png} 
\label{fig:3}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[h!]
\caption{Distribution of the four types of children.}
\includegraphics[width=\textwidth]{PirChart2.png} 
\label{fig:dist}
\end{figure}
\end{center}

\begin{figure}[h!]
\centering
\caption{Chart explaining which synthetic parents and children and when we observe them.}
\begin{tikzpicture}[node distance =2cm]
\node (start) [startstop] {Synthetic Parents: Observed in 1960 to 2000. $25 \leq age \leq 40$, White, with kids};

\node (pro1) [process, below of = start, yshift = -2cm] {Children: Observed between 1994 and 2019. Born between 1954 to 1999 and $25 \leq age \leq 40$};

\draw [arrow] (start) -- (pro1);
\end{tikzpicture}
\label{flowchart1}
\end{figure}

### 2023-05-09 my_paper/tables/tab04-summary-stats.tex
finish implementing the code that would merge synthetic parents (ACS) to children (CPS) addressing Yona's comments

\begin{table}[H]

\caption{Summary statistics of outcomes using parent's place of birth only for those that self-identify as Hispanic \label{tab:c&p2}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcccccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Father's and Mother's Ethnicities} & \multicolumn{2}{c}{Differences} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-7}
Variables & \specialcell{White Father \\ White Mother \\ (WW) \\ (1)} & \specialcell{White Father \\ Hispanic Mother \\ (WH) \\ (2)} & \specialcell{Hispanic Father \\ White Mother \\ (HW) \\ (3)} & \specialcell{Hispanic Father \\ Hispanic Mother \\ (HH) \\ (4)} & \specialcell{HH - WW \\ (5)} & \specialcell{HW - WH \\ (6)}\\
\midrule
\textbf{Panel A: Children's Sunthetic Parent} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hspace{1em}Husband’seducation (Total Years) & \specialcell{13.05\\(2.44)} & \specialcell{12.32\\(3.33)} & \specialcell{10.65\\(4.39)} & \specialcell{8.93\\(4.41)} & \specialcell{-4.11**\\(0.02)} & \specialcell{-1.67**\\(0.04)}\\
\hspace{1em}Wife’seducation (Total Years) & \specialcell{12.74\\(2.12)} & \specialcell{11.03\\(3.92)} & \specialcell{11.54\\(3.12)} & \specialcell{8.6\\(4.13)} & \specialcell{-4.13**\\(0.02)} & \specialcell{0.51**\\(0.04)}\\
\hspace{1em}Total Household seducation (Total Years) & \specialcell{25.78\\(4.08)} & \specialcell{23.35\\(6.51)} & \specialcell{22.19\\(6.69)} & \specialcell{17.54\\(7.83)} & \specialcell{-8.25**\\(0.03)} & \specialcell{-1.16*\\(0.07)}\\
\textbf{Panel B: Education} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\addlinespace
\hspace{1em}Men’s education (Total Years) & \specialcell{12.97\\(2.15)} & \specialcell{13.45\\(2.37)} & \specialcell{13.13\\(2.27)} & \specialcell{12.89\\(2.25)} & \specialcell{-0.08**\\(0.01)} & \specialcell{-0.32**\\(0.03)}\\
\hspace{1em}Women’s education (Total Years) & \specialcell{13.23\\(2.25)} & \specialcell{13.75\\(2.41)} & \specialcell{13.32\\(2.34)} & \specialcell{13.26\\(2.37)} & \specialcell{0.03**\\(0.01)} & \specialcell{-0.43**\\(0.03)}\\
\textbf{Panel C: Children's Employment and Earnings} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hspace{1em}Men’s Employment Rate & \specialcell{0.93\\(0.26)} & \specialcell{0.94\\(0.23)} & \specialcell{0.92\\(0.27)} & \specialcell{0.93\\(0.26)} & \specialcell{0.00***\\(0.00)} & \specialcell{-0.02***\\(0.00)}\\
\hspace{1em}Women’s Employment Rate & \specialcell{0.94\\(0.25)} & \specialcell{0.94\\(0.23)} & \specialcell{0.93\\(0.26)} & \specialcell{0.94\\(0.24)} & \specialcell{0.00***\\(0.00)} & \specialcell{-0.02***\\(0.00)}\\
\addlinespace
\hspace{1em}Men’s Log Hourly Earnings & \specialcell{2.4\\(0.44)} & \specialcell{2.41\\(0.45)} & \specialcell{2.4\\(0.44)} & \specialcell{2.41\\(0.43)} & \specialcell{0.01***\\(0.01)} & \specialcell{-0.01**\\(0.02)}\\
\hspace{1em}Women’s Log Hourly Earnings & \specialcell{2.26\\(0.43)} & \specialcell{2.32\\(0.45)} & \specialcell{2.27\\(0.45)} & \specialcell{2.3\\(0.41)} & \specialcell{0.04***\\(0.01)} & \specialcell{-0.05**\\(0.02)}\\
\hspace{1em}Men’s Log Annual Earnings & \specialcell{10.02\\(1.02)} & \specialcell{10.06\\(1.06)} & \specialcell{10.03\\(0.99)} & \specialcell{10\\(1.04)} & \specialcell{-0.02**\\(0.01)} & \specialcell{-0.03**\\(0.04)}\\
\hspace{1em}Women’s Log Annual Earnings & \specialcell{9.44\\(1.59)} & \specialcell{9.55\\(1.59)} & \specialcell{9.47\\(1.55)} & \specialcell{9.52\\(1.52)} & \specialcell{0.08**\\(0.02)} & \specialcell{-0.08*\\(0.05)}\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[1] Source: The 1970-1990 Census for synthetic parents, and 1994-2019 Current Population Surveys (CPS) for children's outcomes
\item[2] The data is restricted to native-born United States citizens between 1994 and 2019 who are also White and between the ages of 25 and 40, and who identify as Hispanic. I identify the ethnicity of a person's parents through the parent's place of birth. A parent is Hispanic if they were born in a Spanish-speaking country. A parent is White if they were born in the United States.
\end{tablenotes}
\end{threeparttable}}
\end{table}

>>>>

\begin{landscape}
\begin{ThreePartTable}
\begin{TableNotes}
\item[1] Source: The 1950-2000 Census for synthetic parents, and 1994-2019 Current Population Surveys (CPS) for children's outcomes
\item[2] The data is restricted to native-born United States citizens between 1994 and 2019 who are also White and between the ages of 25 and 40. I identify the ethnicity of a person's parents through the parent's place of birth. A parent is Hispanic if they were born in a Spanish-speaking country. A parent is White if they were born in the United States.
\end{TableNotes}
\begin{longtable}[t]{>{\raggedright\arraybackslash}p{5cm}cccccc}
\caption{Summary statistics of outcomes using parent's place of birth only for those that self-identify as Hispanic \label{tab:c&p2}}\\
\toprule
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Father's and Mother's Ethnicities} & \multicolumn{2}{c}{Differences} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-7}
Variables & \specialcell{White \\ White \\ (WW) \\ (1)} & \specialcell{White \\ Hispanic \\ (WH) \\ (2)} & \specialcell{Hispanic \\ White \\ (HW) \\ (3)} & \specialcell{Hispanic \\ Hispanic \\ (HH) \\ (4)} & \specialcell{HH - WW \\ (5)} & \specialcell{HW - WH \\ (6)}\\
\midrule
\endfirsthead
\caption[]{Summary statistics of outcomes using parent's place of birth only for those that self-identify as Hispanic  \textit{(continued)}}\\
\toprule
Variables & \specialcell{White \\ White \\ (WW) \\ (1)} & \specialcell{White \\ Hispanic \\ (WH) \\ (2)} & \specialcell{Hispanic \\ White \\ (HW) \\ (3)} & \specialcell{Hispanic \\ Hispanic \\ (HH) \\ (4)} & \specialcell{HH - WW \\ (5)} & \specialcell{HW - WH \\ (6)}\\
\midrule
\endhead
\midrule
\multicolumn{7}{r@{}}{\textit{(Continued on Next Page...)}}\
\endfoot
\bottomrule
\insertTableNotes
\endlastfoot
\textbf{Panel A: Children's Education} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hspace{1em}Men’s education (Total Years) & \specialcell{13.82\\(2.42)} & \specialcell{13.4\\(2.38)} & \specialcell{13.08\\(2.27)} & \specialcell{12.87\\(2.3)} & \specialcell{-0.94***\\(0.01)} & \specialcell{-0.32**\\(0.03)}\\
\hspace{1em}Women’s education (Total Years) & \specialcell{14.06\\(2.37)} & \specialcell{13.62\\(2.39)} & \specialcell{13.26\\(2.35)} & \specialcell{13.22\\(2.39)} & \specialcell{-0.84***\\(0.01)} & \specialcell{-0.36**\\(0.02)}\\
\textbf{Panel B: Children's Employment and Earnings} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hspace{1em}Men’s Unemployment Rate & \specialcell{0.04\\(0.8)} & \specialcell{0.06\\(0.76)} & \specialcell{0.07\\(0.74)} & \specialcell{0.07\\(0.75)} & \specialcell{0.02***\\(0.00)} & \specialcell{0.01***\\(0.00)}\\
\addlinespace
\hspace{1em}Women’s Unemployment Rate & \specialcell{0.04\\(0.81)} & \specialcell{0.06\\(0.24)} & \specialcell{0.07\\(0.75)} & \specialcell{0.06\\(0.76)} & \specialcell{0.02***\\(0.00)} & \specialcell{0.01***\\(0.00)}\\
\hspace{1em}Men’s Log Hourly Earnings & \specialcell{2.51\\(0.45)} & \specialcell{2.43\\(0.46)} & \specialcell{2.42\\(0.44)} & \specialcell{2.42\\(0.43)} & \specialcell{-0.09***\\(0)} & \specialcell{-0.00**\\(0.02)}\\
\hspace{1em}Women’s Log Hourly Earnings & \specialcell{2.32\\(0.49)} & \specialcell{2.31\\(0.45)} & \specialcell{2.28\\(0.45)} & \specialcell{2.31\\(0.42)} & \specialcell{-0.02***\\(0)} & \specialcell{-0.03**\\(0.02)}\\
\hspace{1em}Men’s Log Annual Earnings & \specialcell{10.29\\(1.01)} & \specialcell{10.09\\(1.05)} & \specialcell{10.06\\(0.97)} & \specialcell{10.01\\(1.04)} & \specialcell{-0.28***\\(0.01)} & \specialcell{-0.03**\\(0.03)}\\
\hspace{1em}Women’s Log Annual Earnings & \specialcell{9.43\\(1.77)} & \specialcell{9.52\\(1.59)} & \specialcell{9.47\\(1.56)} & \specialcell{9.53\\(1.49)} & \specialcell{0.1**\\(0.02)} & \specialcell{-0.05*\\(0.05)}\\*
\end{longtable}
\end{ThreePartTable}
\end{landscape}

### 2023-05-09 output/tables/tab03a-summary-stats.tex
table edits
finish implementing the code that would merge synthetic parents (ACS) to children (CPS) addressing Yona's comments

\caption{Summary statistics of synthetic parents by couple type \label{tab:synth}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcccccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Father's and Mother's Ethnicities} & \multicolumn{2}{c}{Differences} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-7}
Variables & \specialcell{White \\ White \\ (WW) \\ (1)} & \specialcell{White \\ Hispanic \\ (WH) \\ (2)} & \specialcell{Hispanic \\ White \\ (HW) \\ (3)} & \specialcell{Hispanic \\ Hispanic \\ (HH) \\ (4)} & \specialcell{HH - WW \\ (5)} & \specialcell{HW - WH \\ (6)}\\
\midrule
Husband's education (Total Years) & \specialcell{13.05\\(2.44)} & \specialcell{12.32\\(3.33)} & \specialcell{10.65\\(4.39)} & \specialcell{8.93\\(4.41)} & \specialcell{-4.11**\\(0.02)} & \specialcell{-1.67**\\(0.04)}\\
Wife's education (Total Years) & \specialcell{12.74\\(2.12)} & \specialcell{11.03\\(3.92)} & \specialcell{11.54\\(3.12)} & \specialcell{8.6\\(4.13)} & \specialcell{-4.13**\\(0.02)} & \specialcell{0.51**\\(0.04)}\\
Total Household seducation (Total Years) & \specialcell{25.78\\(4.08)} & \specialcell{23.35\\(6.51)} & \specialcell{22.19\\(6.69)} & \specialcell{17.54\\(7.83)} & \specialcell{-8.25**\\(0.03)} & \specialcell{-1.16*\\(0.07)}\\
Log Total Family Income & \specialcell{10.79\\(0.57)} & \specialcell{10.65\\(0.66)} & \specialcell{10.55\\(0.74)} & \specialcell{10.38\\(0.75)} & \specialcell{-0.41***\\(0)} & \specialcell{-0.1***\\(0.01)}\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[1] Source: The 1970-1990 Census for synthetic parents, and 1994-2019 Current Population Surveys (CPS) for children's outcomes
\item[2] The data is restricted to native-born United States citizens between 1994 and 2019 who are also White and between the ages of 25 and 40. I identify the ethnicity of a person's parents through the parent's place of birth. A parent is Hispanic if they were born in a Spanish-speaking country. A parent is White if they were born in the United States.
\end{tablenotes}
\end{threeparttable}}
\end{table}

>>>>

\caption{Summary statistics of synthetic parents by couple type \label{tab:synth}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{5cm}cccccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Father's and Mother's Ethnicities} & \multicolumn{2}{c}{Differences} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-7}
Variables & \specialcell{White \\ White \\ (WW) \\ (1)} & \specialcell{White \\ Hispanic \\ (WH) \\ (2)} & \specialcell{Hispanic \\ White \\ (HW) \\ (3)} & \specialcell{Hispanic \\ Hispanic \\ (HH) \\ (4)} & \specialcell{HH - WW \\ (5)} & \specialcell{HW - WH \\ (6)}\\
\midrule
Husband's education (Total Years) & \specialcell{12.75\\(0.61)} & \specialcell{11.77\\(1.87)} & \specialcell{10.25\\(2.44)} & \specialcell{8.64\\(2.01)} & \specialcell{-4.11***\\(0.00)} & \specialcell{-1.52***\\(0.00)}\\
Wife's education (Total Years) & \specialcell{12.47\\(0.56)} & \specialcell{10.40\\(2.23)} & \specialcell{11.11\\(1.75)} & \specialcell{8.49\\(1.92)} & \specialcell{-3.98***\\(0.00)} & \specialcell{0.70***\\(0.00)}\\
Total Household seducation (Total Years) & \specialcell{25.22\\(1.17)} & \specialcell{22.17\\(4.05)} & \specialcell{21.36\\(4.10)} & \specialcell{17.13\\(3.88)} & \specialcell{-8.09***\\(0.00)} & \specialcell{-0.81***\\(0.01)}\\
Log Total Family Income & \specialcell{10.72\\(0.09)} & \specialcell{10.55\\(0.26)} & \specialcell{10.46\\(0.27)} & \specialcell{10.27\\(0.21)} & \specialcell{-0.45***\\(0.00)} & \specialcell{-0.10***\\(0.00)}\\
Fertility & \specialcell{3.77\\(0.40)} & \specialcell{3.98\\(0.71)} & \specialcell{4.15\\(0.79)} & \specialcell{4.23\\(0.64)} & \specialcell{0.46***\\(0.00)} & \specialcell{0.17***\\(0.00)}\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[1] Source: The 1950-2000 Census for synthetic parents, and 1994-2019 Current Population Surveys (CPS) for children's outcomes
\item[2] The data is restricted to native-born United States citizens who are also White, between the ages of 25 and 40, and have kids. I identify the ethnicity of a person's parents through the parent's place of birth. A parent is Hispanic if they were born in a Spanish-speaking country. A parent is White if they were born in the United States.
\end{tablenotes}
\end{threeparttable}}
\end{table}

### 2023-05-09 output/tables/tab03b-summary-stats.tex
finish implementing the code that would merge synthetic parents (ACS) to children (CPS) addressing Yona's comments

\item[1] Source: The 1970-1990 Census for synthetic parents, and 1994-2019 Current Population Surveys (CPS) for children's outcomes
\item[2] The data is restricted to native-born United States citizens between 1994 and 2019 who are also White and between the ages of 25 and 40. I identify the ethnicity of a person's parents through the parent's place of birth. A parent is Hispanic if they were born in a Spanish-speaking country. A parent is White if they were born in the United States.

@@

\hspace{1em}Men’s education (Total Years) & \specialcell{13.91\\(2.39)} & \specialcell{13.58\\(2.35)} & \specialcell{13.21\\(2.32)} & \specialcell{12.91\\(2.26)} & \specialcell{-1.00***\\(0.01)} & \specialcell{-0.36**\\(0.03)}\\
\hspace{1em}Women’s education (Total Years) & \specialcell{14.29\\(2.41)} & \specialcell{13.87\\(2.47)} & \specialcell{13.42\\(2.35)} & \specialcell{13.27\\(2.37)} & \specialcell{-1.01***\\(0.01)} & \specialcell{-0.46**\\(0.03)}\\

@@

\hspace{1em}Men’s Unemployment Rate & \specialcell{0.05\\(0.78)} & \specialcell{0.06\\(0.77)} & \specialcell{0.08\\(0.74)} & \specialcell{0.07\\(0.74)} & \specialcell{0.02***\\(0.00)} & \specialcell{0.02***\\(0.00)}\\

@@

\hspace{1em}Women’s Unemployment Rate & \specialcell{0.04\\(0.8)} & \specialcell{0.05\\(0.22)} & \specialcell{0.07\\(0.75)} & \specialcell{0.06\\(0.76)} & \specialcell{0.02***\\(0.00)} & \specialcell{0.02***\\(0.00)}\\
\hspace{1em}Men’s Log Hourly Earnings & \specialcell{2.48\\(0.45)} & \specialcell{2.41\\(0.45)} & \specialcell{2.4\\(0.44)} & \specialcell{2.41\\(0.43)} & \specialcell{-0.07***\\(0.01)} & \specialcell{-0.00**\\(0.02)}\\
\hspace{1em}Women’s Log Hourly Earnings & \specialcell{2.33\\(0.49)} & \specialcell{2.33\\(0.46)} & \specialcell{2.27\\(0.45)} & \specialcell{2.3\\(0.41)} & \specialcell{-0.02***\\(0.01)} & \specialcell{-0.06**\\(0.02)}\\
\hspace{1em}Men’s Log Annual Earnings & \specialcell{10.25\\(1.01)} & \specialcell{10.08\\(1.05)} & \specialcell{10.04\\(1.06)} & \specialcell{10.01\\(1.04)} & \specialcell{-0.25**\\(0.01)} & \specialcell{-0.04**\\(0.03)}\\
\hspace{1em}Women’s Log Annual Earnings & \specialcell{9.46\\(1.78)} & \specialcell{9.54\\(1.64)} & \specialcell{9.47\\(1.57)} & \specialcell{9.53\\(1.52)} & \specialcell{0.07**\\(0.02)} & \specialcell{-0.07*\\(0.06)}\\

@@

\hspace{1em}Men & \specialcell{0.05} & \specialcell{0.81} & \specialcell{0.88} & \specialcell{0.97} &  & \\
\hspace{1em}Women & \specialcell{0.06} & \specialcell{0.85} & \specialcell{0.87} & \specialcell{0.97} &  & \\*

>>>>

\item[1] Source: The 1950-2000 Census for synthetic parents, and 1994-2019 Current Population Surveys (CPS) for children's outcomes
\item[2] The data is restricted to native-born United States citizens who are also White and between the ages of 25 and 40. I identify the ethnicity of a person's parents through the parent's place of birth. A parent is Hispanic if they were born in a Spanish-speaking country. A parent is White if they were born in the United States.

@@

\hspace{1em}Men’s education (Total Years) & \specialcell{13.82\\(2.42)} & \specialcell{13.58\\(2.40)} & \specialcell{13.22\\(2.34)} & \specialcell{12.90\\(2.31)} & \specialcell{-0.92***\\(0.01)} & \specialcell{-0.36**\\(0.02)}\\
\hspace{1em}Women’s education (Total Years) & \specialcell{14.06\\(2.37)} & \specialcell{13.79\\(2.44)} & \specialcell{13.42\\(2.38)} & \specialcell{13.24\\(2.39)} & \specialcell{-0.82***\\(0.01)} & \specialcell{-0.37**\\(0.02)}\\

@@

\hspace{1em}Men’s Unemployment Rate & \specialcell{0.04\\(0.80)} & \specialcell{0.05\\(0.77)} & \specialcell{0.07\\(0.75)} & \specialcell{0.07\\(0.75)} & \specialcell{0.02***\\(0.00)} & \specialcell{0.01***\\(0.00)}\\

@@

\hspace{1em}Women’s Unemployment Rate & \specialcell{0.04\\(0.81)} & \specialcell{0.05\\(0.22)} & \specialcell{0.06\\(0.76)} & \specialcell{0.06\\(0.76)} & \specialcell{0.02***\\(0.00)} & \specialcell{0.01***\\(0.00)}\\
\hspace{1em}Men’s Log Hourly Earnings & \specialcell{2.51\\(0.45)} & \specialcell{2.44\\(0.47)} & \specialcell{2.43\\(0.45)} & \specialcell{2.42\\(0.43)} & \specialcell{-0.09***\\(0.00)} & \specialcell{-0.01**\\(0.01)}\\
\hspace{1em}Women’s Log Hourly Earnings & \specialcell{2.32\\(0.49)} & \specialcell{2.32\\(0.46)} & \specialcell{2.29\\(0.46)} & \specialcell{2.31\\(0.42)} & \specialcell{-0.02***\\(0.00)} & \specialcell{-0.03**\\(0.01)}\\
\hspace{1em}Men’s Log Annual Earnings & \specialcell{10.29\\(1.01)} & \specialcell{10.12\\(1.05)} & \specialcell{10.08\\(1.01)} & \specialcell{10.01\\(1.04)} & \specialcell{-0.28***\\(0.01)} & \specialcell{-0.04**\\(0.03)}\\
\hspace{1em}Women’s Log Annual Earnings & \specialcell{9.43\\(1.77)} & \specialcell{9.51\\(1.63)} & \specialcell{9.46\\(1.59)} & \specialcell{9.53\\(1.50)} & \specialcell{0.10**\\(0.02)} & \specialcell{-0.05**\\(0.05)}\\

@@

\hspace{1em}Men & \specialcell{0.04} & \specialcell{0.74} & \specialcell{0.83} & \specialcell{0.96} &  & \\
\hspace{1em}Women & \specialcell{0.05} & \specialcell{0.78} & \specialcell{0.82} & \specialcell{0.97} &  & \\*

### 2023-05-09 output/tables/tab06-regression.tex
finish implementing the code that would merge synthetic parents (ACS) to children (CPS) addressing Yona's comments

\caption{Effect of Having Hispanic Last Name \label{tab:identreg}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcc}
\toprule
  & \specialcell{(1) \\ Log annual earnings} & \specialcell{(2) \\  Log annual earnings}\\
\midrule
$HW_{i} \times Hispanic_{i}$ & \num{-0.02} & \num{-0.02}\\
 & (\num{0.08}) & (\num{0.07})\\
$Hispanic_{i}$ & \num{-0.11}** & \num{-0.06}\\
 & (\num{0.05}) & (\num{0.05})\\
$HW_{i}$ & \num{-0.03} & \num{0.00}\\
 & (\num{0.08}) & (\num{0.06})\\
\midrule
State FE & X & X\\
Year FE & X & X\\
\textit{Controlling for:} &  & \\
Hours Worked & X & X\\
Age & X & X\\
Education &  & X\\
Observations & \num{2423} & \num{2423}\\
\bottomrule
\multicolumn{3}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] \footnotesize{This table includes the estimation results of equation (\ref{eq:iden}).}
\item[2] \footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother, and Hispanic is an indicator variable that is equal to one if a person self-identifies as Hispanic.}
\item[3] \footnotesize{The sample is restricted to men working full-time full-year and are waged and salaried workers.}
\item[4] \footnotesize{Column one has the regression results when controlling for hours worked, age, and fixed effects. Column two has the results after controlling for education.}
\end{tablenotes}
\end{threeparttable}}
\end{table}

>>>>

\caption{Effect of Having Hispanic Last Name by Hispanic Identity\label{tab:identreg}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lccccc}
\toprule
  & \specialcell{(1) \\ Log annual \\ earnings} & \specialcell{(2) \\ Log annual \\ earnings} & \specialcell{(3) \\ Log annual \\ earnings} & \specialcell{(4) \\  Log annual \\ earnings} & \specialcell{(5) \\  Log annual \\ earnings}\\
\midrule
$HW_{ist} \times Hispanic_{ist}$ & \num{-0.09} & \num{-0.06} & \num{-0.05} & \num{-0.04} & \num{-0.04}\\
 & (\num{0.07}) & (\num{0.07}) & (\num{0.06}) & (\num{0.06}) & (\num{0.06})\\
$Hispanic_{ist}$ & \num{-0.13}** & \num{-0.11} & \num{-0.09}** & \num{-0.03} & \num{-0.02}\\
 & (\num{0.07}) & (\num{0.07}) & (\num{0.04}) & (\num{0.05}) & (\num{0.04})\\
$HW_{ist}$ & \num{0.03} & \num{0.01} & \num{0.00} & \num{0.02} & \num{0.02}\\
 & (\num{0.06}) & (\num{0.06}) & (\num{0.06}) & (\num{0.06}) & (\num{0.05})\\
Constant & \num{10.53}*** & \num{9.57}*** &  &  & \\
 & (\num{0.05}) & (\num{0.08}) &  &  & \\
\midrule
$HW_{ist} \times Hispanic_{ist} + HW_{ist}$ & -0.06*** & -0.05** & -0.05** & -0.02 & -0.01\\
 & (0.02) & (0.02) & (0.02) & (0.02) & (0.02)\\
\midrule
\textit{Controlling for:} &  &  &  &  & \\
Hours Worked &  & X & X & X & X\\
State FE &  &  & X & X & X\\
Year FE &  &  & X & X & X\\
Age FE &  &  & X & X & X\\
Education FE &  &  &  & X & X\\
Parental Background &  &  &  &  & X\\
Observations & \num{3581} & \num{3581} & \num{3581} & \num{3581} & \num{3581}\\
\bottomrule
\multicolumn{6}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] \footnotesize{This table includes the estimation results of equation (\ref{eq:iden}).}
\item[2] \footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother, and Hispanic is an indicator variable that is equal to one if a person self-identifies as Hispanic.}
\item[3] \footnotesize{The sample is restricted to men working full-time full-year and are waged and salaried workers.}
\item[4] \footnotesize{Column one has the regression results when controlling for hours worked, age, education, year and state fixed effects. Column two has the results after controlling for education.}
\item[5] {\setstretch{1.0}\footnotesize{Standard errors are clustered on the state level.}}
\end{tablenotes}
\end{threeparttable}}
\end{table}
